ms_figures

### 2023-04-28 ms_figures.Rmd
add lims to fig 3 and update text

fig3c <- fig3c_data %>%
  ggplot(aes(x = year, y = supply_percent, color = supply_source)) +
  geom_line() +
  scale_color_manual(values = c("#F37542", "#0F2D59")) +
  labs(x = "", y = "Percent of supply", color = "Origin") +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

@@

fig3d <- fig3d_data %>%
  ggplot(aes(x = year, y = supply_percent, color = supply_source)) +
  geom_line() +
  scale_color_manual(values = c("#F37542", "#0F2D59")) +
  labs(x = "", y = "Percent of supply", color = "Origin") +
  facet_wrap(~region) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        strip.background = element_blank())

>>>>

fig3c <- fig3c_data %>%
  ggplot(aes(x = year, y = supply_percent, color = supply_source)) +
  geom_line() +
  scale_color_manual(values = c("#F37542", "#0F2D59")) +
  labs(x = "", y = "Percent of supply", color = "Origin") +
  lims(y = c(0,100)) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

@@

fig3d <- fig3d_data %>%
  ggplot(aes(x = year, y = supply_percent, color = supply_source)) +
  geom_line() +
  scale_color_manual(values = c("#F37542", "#0F2D59")) +
  labs(x = "", y = "Percent of supply", color = "Origin") +
  facet_wrap(~region) +
  lims(y = c(0,100)) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        strip.background = element_blank())
